---
title: "ECON 121 FA25 Problem Set 1"
author: "Your name"
output: html_document # change to pdf_document if you have LaTeX
---

```{r setup, include=FALSE}
rm(list = ls()) # clears the environment
library("tidyverse") # load tidyverse
ssa <- read_csv("https://github.com/tomvogl/econ121/raw/main/data/ssa_names.csv") # load dataset
```

## Question 1

Verbal: list group members.

\newpage

## Question 2

Code: Summarize the data.

Verbal: Interpret the summary statistics.

```{r}
# Question 2 code here

```

\newpage

## Question 3

Code: Find the all time most common boy and girl names.

Verbal: Interpret your results.

```{r}
# Question 3 code here

```

\newpage

## Question 4

Code: Plot time trends in the number of unique names by sex

Verbal: Interpret your results.

```{r}
# Question 4 code here

```

\newpage

## Question 5

Code: Plot time trends in the number of unique names relative to the number of 
babies by sex.

Verbal: Interpret your results.

```{r}
# Question 5 code here

```

\newpage

## Question 6

Verbal: Which names and why?

\newpage

## Question 7

Code: Find all-time frequency of your names and compare with all-time most
popular names.

Verbal: Interpret your results.

```{r}
# Question 7 code here

```

\newpage

## Question 8

Code: Graph the annual frequencies of your chosen name(s) over time.

Verbal: Interpret your results.

```{r}
# Question 8 code here

```

