---
title: "ECON 121 FA25 Problem Set 2"
author: "Your name"
output: html_document # change to pdf_document if you have LaTeX
---

```{r setup, include=FALSE}
rm(list = ls()) # clears the environment
library(tidyverse) # for data manipulation and summary statistics
library(fixest) # for regression
library(marginaleffects) # for linear and non-linear combinations of coefficients
load(url("https://github.com/tomvogl/econ121/raw/main/data/cps18.rds")) # load CPS data
load(url("https://github.com/tvogl/econ121/raw/main/data/nlsy79.rds")) # load NLSY data
```

## Question 1

Verbal: list group members, if you have them.

\newpage

## Question 2

Verbal answer only, no code.

\newpage

## Question 3

Code: Summarize data.

Verbal: Interpret the summary statistics.

```{r}
# All question 3 code here

```

\newpage

## Question 4

Code: Estimate regression.

Verbal: Interpret your results.

```{r}
# All question 4 code here

```

\newpage

## Question 5

Code: Estimate regression.

Verbal: Interpret your results.

```{r}
# All question 5 code here

```

\newpage

## Question 6

Code: Assess statistical significance.

Verbal: Interpret your results.

```{r}
# All question 6 code here

```

\newpage

## Question 7

Code: Estimate regressions and assess significance of differences between them.

Verbal: Interpret your results.

```{r}
# All question 7 code here

```

\newpage

## Question 8

Code: Estimate regression, use delta method.

Verbal: Interpret your results.

```{r}
# All question 8 code here

```

\newpage

## Question 9

Code: Load dataset, compute unweighted and weighted means.

Verbal: Interpret your results.

```{r}
# All question 9 code here

```

\newpage

## Question 10

Code: Modify sample, estimate unweighted and weighted regressions.

Verbal: Assess unweighted versus weighted results.

```{r}
# All question 10 code here

```

\newpage

## Question 11

Verbal answer only, no code.

\newpage

## Question 12

Verbal answer only, no code.

\newpage

## Question 13

Code: Estimate regression.

Verbal: Explain choice of covariates, interpret results.

```{r}
# All question 13 code here

```

