---
title: "ECON 121 FA23 Problem Set 4"
author: "Your name"
output: html_document # change to pdf_document if you have LaTeX
---

```{r setup, include=FALSE}
rm(list = ls()) # clears the environment
library(tidyverse) # for data manipulation and summary statistics
library(fixest) # for regression
load(url("https://github.com/tomvogl/econ121/raw/main/data/nlsy_kids.rds"))
```

## Question 1

Verbal: list group members.

\newpage

## Question 2

Code: Load packages and dataset, summarize data.

Verbal: Interpret the summary statistics.

```{r message=FALSE, warning=FALSE}
# The PDF will show the code you write here but not the output.
# Load packages and dataset here.

```

```{r}
# The PDF will show the code AND output here.
# Summarize the data here.

```

\newpage

## Question 3

Code: Regression.

Verbal: Interpret.

```{r}
# All question 3 code here.

```

\newpage

## Question 4

Code: Regression.

Verbal: Interpret.

```{r}
# All question 4 code here

```

\newpage

## Question 5

Code: Regression.

Verbal: Interpret.

```{r}
# All question 5 code here

```

\newpage

## Question 6

Code: Regression.

Verbal: Interpret.

```{r}
# All question 6 code here

```

\newpage

## Question 7

Code: Regressions.

Verbal: Interpret.

```{r}
# All question 7 code here

```

\newpage

## Question 8

Code: Regressions.

Verbal: Interpret.

```{r}
# All question 8 code here

```

\newpage

## Question 9

Code: Analysis of heterogeneity.

Verbal: Interpret.

```{r}
# All question 9 code here

```

\newpage

## Question 9

Verbal: Policy implications.

