---
title: "ECON 121 FA23 Problem Set 5"
author: "Your name"
output: html_document # change to pdf_document if you have LaTeX
---

```{r setup, include=FALSE}
rm(list = ls()) # clears the environment
library(tidyverse) # for data manipulation and summary statistics
library(fixest) # for regression
crime <- read_csv("https://github.com/tomvogl/econ121/raw/main/data/crime_argentina.csv")
```

## Question 1

Verbal: list group members.

\newpage

## Question 2

Code: Load packages and dataset, summarize data.

Verbal: Interpret summary statistics.

```{r}
# All question 2 code here.

```

\newpage

## Question 3

Code: Regression.

Verbal: Interpret.

```{r}
# All question 3 code here.

```

\newpage

## Question 4

Code: Generate variable.

```{r}
# All question 4 code here

```

\newpage

## Question 5

Code: Regression.

Verbal: Interpret.

```{r}
# All question 5 code here

```

\newpage

## Question 6

Code: Regression.

Verbal: Interpret.

```{r}
# All question 6 code here

```

\newpage

## Question 7

Code: Calculation. 

Verbal: Interpret.

```{r}
# All question 7 code here

```

\newpage

## Question 8

Code: Regression.

Verbal: Interpret.

```{r}
# All question 8 code here

```

\newpage

## Question 9

Verbal: Assessment.

\newpage

## Question 10

Verbal: Interpretation.

\newpage

## Question 11

# a.

Code.

```{r}

```

# b. code

```{r}

```

# c. code and verbal

```{r}

```

# d. code and verbal

```{r}

```

# e. code and verbal

```{r}

```

# f. verbal

