---
title: "ECON 121 FA25 Final Exam"
author: "Your name and PID"
output: html_document # change to pdf_document if you have LaTeX
---

```{r setup, include=FALSE}
rm(list = ls())
library(tidyverse)
library(fixest)
library(marginaleffects)
load(url("https://github.com/tomvogl/econ121/raw/main/data/finance.rds"))
```

## Question 1

```{r}
# Code here
```

\newpage

# Question 2

```{r}
# Code here
```

\newpage

## Question 3

```{r}
# Code here
```

\newpage

## Question 4

Verbal answer here.

\newpage

## Question 5

```{r}
# Code here
```

\newpage

## Question 6

Verbal answer here.

\newpage

## Question 7

```{r}
# Code here
```

\newpage

## Question 8

Verbal answer here.

\newpage

## Question 9

```{r}
# Code here
```

\newpage

## Question 10

Verbal answer here.

\newpage

## Question 11

```{r}
# Code here
```

\newpage

## Question 12

Verbal answer here.

\newpage

## Question 13

```{r}
# Code here
```

\newpage

## Question 14

Verbal answer here.

\newpage

## Question 15

```{r}
# Code here
```

\newpage

## Question 16

```{r}
# Code here
```

\newpage

## Question 17

Verbal answer here.

\newpage

## Question 18

Verbal answer here.

\newpage

## Question 19

```{r}
# Code here
```

\newpage

## Question 20

Verbal answer OR code.

```{r}
# Code here if applicable
```







