---
title: "ECON 121 FA25 Practice Final Exam"
author: "Your name"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list = ls())
library(tidyverse)
library(fixest)
library(marginaleffects)
load(url("https://github.com/tomvogl/econ121/raw/main/data/migration.rds"))
```

## Question 1

```{r}
# Your code here
```

\newpage

## Question 2

Your verbal answer here

\newpage

## Question 3

```{r}
# Your code here
```

\newpage

## Question 4

```{r}
# Your code here
```

\newpage

## Question 5

Your verbal answer here

\newpage

## Question 6

```{r}
# Your code here
```

\newpage

## Question 7

```{r}
# Your code here
```

\newpage

## Question 8

```{r}
# Your code here
```

\newpage

## Question 9

Your verbal answer here

\newpage

## Question 10

```{r}
# Your code here
```

\newpage

## Question 11

```{r}
# Your code here
```

\newpage

## Question 12

Your verbal answer here

\newpage

## Question 13

```{r}
# Your code here
```

\newpage

## Question 14

Your verbal answer here

\newpage

## Question 15

Your verbal answer here

\newpage

## Question 16

Your verbal answer here

\newpage

## Question 17

```{r}
# Your code here
```

\newpage

## Question 18

Your verbal answer here

\newpage

## Question 19

```{r}
# Your code here
```

\newpage

## Question 20

Your verbal answer here







